
\section{Introduction}

Home automation system in simple terms refers to automation of day
to day appliances that is used in homes. Automation of homes can be
divided into two broad categories:

\begin{enumerate}[nosep]
  \item Controlling
  \item Monitoring
\end{enumerate}

Home automation is achieved through either monitoring or controlling.
In our project we try to cover both monitoring and controlling and a
combination of both.

Home automation satisfies the resident’s needs and desires by making
it more convenient to adjust or control attributes such as lighting,
temperature, entertainment systems, and other electrical as well as
non-electrical appliances. In addition to that, home automation may
also include safety and security of residents.

Home automation can be really advanced and might allow the residents
to control certain parameters in numerous different ways such as
gesture recognition, or sensors or voice commands and so on.
Nonetheless, all these technologies favor in comfort of the residents.

We aim to perform microcontroller based home automation with the help
of wired sensor technology. In our home automation system, devices
will get triggered automatically based on certain conditions so that
the resident won't have to manually control them.

\section{Objectives}

The fundamental objective of this project is to gain a more
comprehensible knowledge about real-time applications of several
electronic components along with a few sensing devices and also to
acquire proper idea about interfacing a micro-controller with various
electronic components.

Specific objectives of our project are as follows:

\begin{enumerate}

  \item Automatic Light Switching based on Visitor Count

    To switch the lights of a room off by counting the number of
    people in the room. If the visitors in a room are 0, the system
    will switch off the lights after a minimum time period has
    elapsed.

  \item Home Security System

    This includes detection and hopefully prevention of possible fire
    accidents. Detect leakage of LPG gas and notify the user in via.
    mobile networking.

    % methodology:
    % When there's leakage of LPG gas in a room, the designed system
    % notifies the owner of the home via text message. GSM is interfaced
    % with arduino, so when the gas leakage detector module senses the
    % leakage, GSM sends message to the owner so as to alert the leakage
    % situation.

  \item Touchless Automated Trash Can

    Design a system such that whenever a motion is detected within the
    range of the sensor it opens the lid of the trash can
    automatically and the lid remains open as long as the sensor
    detects motion.

    % methodology:
    % In the system detects the human approaching it. The closing and
    % opening of the lid is done with the help of motor that is
    % interfaced with arduino.

\end{enumerate}
