\documentclass[fleqn]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4 paper,top=1in,left=1in,footskip=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multicol}
\usepackage{tocloft}
\usepackage[hidelinks,linktoc=all]{hyperref}
\usepackage{lipsum}

\usepackage[export]{adjustbox}

\setlength{\parindent}{0em}
\setlength{\parskip}{1.5em}
\setlength\columnsep{1cm}
\setlength\columnseprule{1pt}

\title{Home Automation System with GSM Support}
\author{Nikin Baidar \\ Namrata Tamang \\ Suhana Chand}
\date{\today}

\begin{document}

\maketitle

\tableofcontents
\addcontentsline{}{}{}
\addtocontents{toc}{~\hfill\textbf{Page}\par}


\include{intro-and-objectives}
\include{method-and-Materials}
\section{Expected Outcome}

We expect the following outcomes on completion of our project:

\begin{enumerate}

  \item With the help of ultrasonic sensors we hope to achieve the
    number of visitors inside a room with at least 90\% accuracy.  And
    based on that visitor count, we have anticipated that the lights
    will get automatically turned off after a certain delay when all
    the number of visitors inside the room is zero.

  \item We have expected our GSM based home security system to
    broadcast an SMS to the mobile phone of the dweller, whenever
    there is an LPG has leakage so as to alert the leakage situation
    and help the person take preventive measures.

  \item The touchless trash can is designed such that we expect its
    lid to automatically open when the sensor detects the motion in
    its periphery or within its range.

\end{enumerate}

\section{Conclusion Of the Synopsis}

In conclusion, an Arduino UNO based home automation system will be
designed. The mechanism with which we aim to achieve this system are
only explained in brief and design considerations have not been
explicitly highlighted hereby this synopsis. We hope to receive
further guidance and help from the project supervisor on that part of
the project.

Furthermore, since a general idea of what mechanisms will be used for
our system design has been mentioned, we would also like to reflect on
the materials or components that we will require for completion of
this project.

The necessary materials are listed in the table below:

\begin{tabular}{|c|c|c|c|}
  \hline

  S.N. & Equipment & Model & Quantity\\
  \hline
  1 &Microcontroller & Arduino UNO & 1\\
  2 &Ultrasonic Sensors & HC-SR04 or any other & 4\\
  3 &LPG Gas Sensor & MP5 or MP6 & 1\\
  4 &Passive IR Sensor  & HC-SR501 or any other &1\\
  5 & 5V Relay Module & $-$ & 1\\
  6 & GSM module & GSM800A SimCom with antenna & 1\\
  7 & Servo Motor & Recommendation required& 1\\
  \hline
\end{tabular}

Beside these equipments, different types of wires and cables along
with other minor circuit  components such as resistors, potentiometer,
capacitors, power supplies and batteries, and a generic bread board is
also required. If possible a trash can with lid should also be
provided.

Finally, suggestions for improvisation and optimization of the system
will be highly appreciated.
\end{document}
